flowers-pilot-analysis

### 2021-07-23 code/aa-flowers-pilot_analysis.Rmd
add code for feedback, contexts, and demographics

```{r set-up, include=F}
library(tidyverse)
library(jsonlite)
library(here)
source(here("code/preprocessing/00_preprocessing_functions.R"))
theme_set(theme_bw())

##Data import constants
date_start=lubridate::ymd('2021-07-19')
image_location=here("figs")

@@

# Pre-process
```{r process-data, message=FALSE, warning=FALSE}
data_list <- c("technical_pilots", "collabmulti_pilot0", 
               "collabmulti_20", "compet_20")
process_all_data(data_list)
join_all_data()
```

```{r read-processed-date, message=FALSE}
d.players <- read_csv(here("data/processed_data/joined_data/players.csv")) %>% distinct()
d.games <- read_csv(here("data/processed_data/joined_data/games.csv")) %>% distinct()
d.rounds <- read_csv(here("data/processed_data/joined_data/rounds.csv")) %>% distinct()
d.raw_chat <- read_csv(here("data/processed_data/joined_data/raw_chat.csv")) %>% distinct()
```

```{r}
#exclude BLOCKS with <12 completed (all 3 participants responded) rounds
rounds_exclude <- d.rounds %>% group_by(gameId, blockNum) %>% tally() %>% filter(n!=36) %>% select(gameId,blockNum)

@@

```{r}
game_completion <- d.round_results %>% 
  group_by(gameId) %>% 
  summarize(num_rounds=max(trialNum+1)) %>% 
  left_join(d.games%>% ungroup() %>% select(gameId, condition, chat=chatEnabled, gameLength)) %>%
  mutate(gameComplete = ifelse(num_rounds == 48, TRUE, FALSE))
#knitr::kable(summary)
message("Full games")
game_completion %>% filter(num_rounds==48)
message("Partial games")
game_completion %>% filter(num_rounds!=48) 
```

```{r}
d.chat.raw <- d.round_results.raw %>%
  filter(createdAt >= date_start) %>%
  anti_join(rounds_exclude) %>%
  #there will always be an alert for each active round, so drop NA
  filter(!is.na(chat))%>%
  select(-c(ends_with('response'), ends_with('time'), ends_with('utility'), context, stageIds)) %>%
  #mutate(chat = ifelse(is.na(chat), '{}', chat)) %>%
  rename(roundID = `_id`) %>%
  mutate(chat = map(chat, .f = ParseJSONColumn)) %>%
  unnest(chat) %>%
  arrange(createdAt, gameId, blockNum, repNum) %>% 
  left_join(d.players %>% select(playerId, name)) %>%
  left_join(d.round_results %>% select(gameId, blockNum, repNum, trialNum, playerId, playerResponse, playerUtility)) %>%
  left_join(d.games %>% select(gameId, condition, chatEnabled)) %>%
  mutate("participantAction" = ifelse(type == "alert", paste(name, "selected", playerResponse, "for", playerUtility, "point(s)"), NA)) %>%
  select(gameId, trialNum, condition, chatEnabled, playerId, name, text, participantAction, everything()) %>%
  write_csv(here(data_location, 'raw_chat.csv'))

#extract the alternative flowers
d.contexts <- read_csv(here(data_location,'rounds.csv'),guess_max=10000) %>% 
  mutate(data.context = map(data.context, 
                            .f = ParseJSONColumn)) %>% 
  select("_id":"data.numPlayers") %>%
  mutate(data.context = map(data.context,
                            function(df) df %>% gather(key, value) %>%
                              mutate(key = gsub('.', '-', key, fixed=TRUE)) %>%
                              separate(key, into = c("label", "key"), sep = "-") %>%
                              spread(key, value))) %>%
  unnest(data.context) %>%
  rename_with(~ gsub("data.", "", .x, fixed = TRUE))
```

Recast games with a language USE condition
If there were fewer than 3 lines of communication, cast langUse = False
```{r}
d.games <- d.games %>% left_join(d.chat.raw %>% group_by(gameId) %>% summarize(numChat = sum(!is.na(text))) %>% 
                                   mutate(langUse = (numChat >5)) %>% select(-numChat)) %>%
  mutate(langUse = ifelse(is.na(langUse), FALSE, langUse)) %>%
#add a toddle for completed games
  left_join(game_completion %>% select(gameId, gameComplete))
```

How often do participants select a flower that is hidden from them?

# Demographics
```{r demographics}
d.exit.survey <- read_csv(here(data_location, 'player-inputs.csv')) %>%
  filter(createdAt >= date_start) %>%
  left_join(d.games, by = c('gameId')) %>%
    rename_with(~ gsub("data.", "", .x, fixed = TRUE))
```
```{r feedback}
d.exit.survey %>% select( language, fair, chatUseful, feedback, time) %>% knitr::kable()
```

# Pretty pictures

Correlation between response time and utility?

```{r}
d.round_results.final %>% left_join(d.games %>% select(gameId, condition, chatEnabled, langUse, gameComplete)) %>%
  mutate(chat = ifelse(chatEnabled, "lang", "nonlang"),
         full_condition = paste0(condition, "-", chat)) %>%
  ggplot(aes(x=time_sec, y = as.numeric(playerUtility), color = full_condition)) + 
  facet_grid(rows = vars(condition), cols = vars(langUse)) +
  geom_point(alpha = .25) + 
  labs(x = "log time (in seconds)",
       y = "individual utility",
       title = "Response time in sec and utility", subtitle =  "each participant, each round")

d.round_results.final %>% left_join(d.games %>% select(gameId, condition, chatEnabled, langUse)) %>%
  mutate(chat = ifelse(chatEnabled, "lang", "nonlang"),
         full_condition = paste0(condition, "-", chat)) %>%
  ggplot(aes(x=log(time_sec), y = as.numeric(playerUtility), color = full_condition)) + 
  facet_grid(rows = vars(condition), cols = vars(langUse)) +
  geom_point(alpha = .25) + 
  labs(x = "log time (in seconds)",
       y = "individual utility",
       title = "Response time in sec (log) and utility", subtitle =  "each participant, each round")
```

Easiest way to do this, is to derive the game start date with the latest participant ready time and the game finishedAt

```{r}
d.round_results.final %>% left_join(d.games %>% select(gameId, condition, chatEnabled, langUse, gameLength, gameComplete)) %>%
  filter(gameComplete) %>%
  mutate(chat = ifelse(chatEnabled, "lang", "nonlang"),
         full_condition = paste0(condition, "-", chat)) %>%
  group_by(gameId, condition, chat, langUse, full_condition, gameLength) %>%
  summarize(totalUtility = sum(playerUtility))%>%
  ggplot(aes(x=gameLength, y = as.numeric(totalUtility), color = full_condition)) + 
  facet_grid(rows = vars(condition), cols = vars(langUse), scales = "free_y") +
  geom_point(alpha = .75) + 
  labs(x = "Game length (in minutes)",
       y = "total points by group",
       title = "Length of game in mins and utility", subtitle =  "per game")

d.round_results.final %>% left_join(d.games %>% select(gameId, condition, chatEnabled, langUse,gameLength, gameComplete)) %>%
  filter(gameComplete) %>%
  mutate(chat = ifelse(chatEnabled, "lang", "nonlang"),
         chatUse = ifelse(langUse, "chatUse", "noChat"),
         full_condition = paste0(condition, "-", chatUse)) %>%
  group_by(gameId, condition, chat, full_condition,gameLength) %>%
  summarize(totalUtility = sum(playerUtility))%>%
  mutate(totalUtility = ifelse(condition=="coopCartel", totalUtility/3, totalUtility)) %>%
  ggplot(aes(x=as.numeric(gameLength, units="mins"), y = as.numeric(totalUtility), color = full_condition)) + 
  #facet_grid(rows = vars(condition), cols = vars(chat), scales = "free_y") +
  geom_point(alpha = .75) + 
  geom_smooth(method=lm, alpha=.3)+
  labs(x = "Game length (in minutes)",
       y = "total points by group",
       title = "Length of game in mins and utility", subtitle =  "per game")

ggsave(paste0(image_location, "/game_length.png"))
```

```{r chat}
#group raw chat by participant
d.chat <- read_csv(here(data_location, "raw_chat.csv"), guess_max=1000) %>% 
  filter(type == "message") %>%
  full_join(d.round_results, c("gameId", "trialNum", "repNum", "playerId", "numPlayers", "blockNum")) %>%
 # filter(!is.chitchat) %>% 
  mutate(text = gsub("\\n", '', fixed = T, text),
         text = gsub("[/?/.]", ' ', text),
         text = str_squish(text),
         utt_length_chars = str_length(text), 
         utt_length_words = str_count(text, "\\W+") + 1) %>% 
  group_by(gameId, blockNum, trialNum, repNum, playerId, numPlayers) %>%
  summarize(text = paste0(text, collapse = ', '),
            total_num_words = sum(utt_length_words),
            total_num_chars = sum(utt_length_chars)) %>%
  anti_join(rounds_exclude)

Pick just one game to look at, make sure the plot is working?
```{r}
condition = "competCartel"

d.chat %>% 
         left_join(d.games %>% select(gameId, createdAt,condition, langUse, chatEnabled, gameComplete)) %>% 
         filter(langUse, gameComplete) %>%
ggplot(aes(x = repNum, y=total_num_words, color = as.factor(playerId))) + 
  geom_jitter(alpha = .5) + 
  facet_grid(cols = vars(blockNum), rows = vars(gameId), scales = "free_y") + 
  geom_smooth(method=glm, formula=y~poly(x,2), alpha=.3)+
  theme(legend.position = "none")+
  labs(title="Cooperative + Lang Used", subtitle = "Number of words", y="Number of words", x="Round number", color="playerId")

ggsave(paste0(image_location, "/words_over_rounds.png"))
```

@@

competcartel will have a max utility = sum(top_3_flowers)
```{r}
d.max_utility <- d.contexts %>% 
  left_join(d.games %>% select(gameId, condition)) %>%
  mutate(utility= as.numeric(utility)) %>%
  group_by(gameId, blockNum, repNum) %>% 
  slice_max(order_by =utility,n = 3)%>%
  summarize(competCartel = sum(utility),
            coopMulti= sum(utility),
            coopCartel = max(utility * 9)) %>% ungroup() %>%
  pivot_longer(cols = c(competCartel, coopMulti, coopCartel), names_to = "condition", values_to = "maxUtility")

d.utility <- d.round_results.final %>%
         left_join(d.games %>% select(gameId, condition, chatEnabled, langUse)) %>% 
  group_by(gameId, blockNum, repNum, trialNum,condition, langUse) %>% 
  summarize(group_utility = sum(as.numeric(playerUtility)))%>% ungroup() %>%
  left_join(d.max_utility) %>%
  mutate(prop_utility = group_utility/maxUtility,
         langUsed = if_else(langUse, "Lang", "Nonlang"))

d.utility %>% 
  ggplot(aes(x = trialNum, y=prop_utility, color = as.factor(gameId))) + 
  geom_point(alpha = .4) + 
  facet_grid(cols = vars(condition), rows = vars(langUsed), scales = "free_y") + 
  #geom_smooth(method=glm, formula=y~poly(x,2), alpha=.3)+
  theme(legend.position = "none")+
  labs(title="Accuracy", y="Group utility/max utility", x="Round number", color="gameId")

ggsave(paste0(image_location, "/accuracy.png"))

d.utility %>% 
  ggplot(aes(x = trialNum, y=prop_utility, color = as.factor(gameId))) + 
  geom_point(alpha = .4) + 
  facet_grid(cols = vars(condition), rows = vars(langUsed), scales = "free_y") + 
  #geom_smooth(method=glm, formula=y~poly(x,2), alpha=.3)+
  theme(legend.position = "none")+
  labs(title="Accuracy", y="Group utility/max utility", x="Round number", color="gameId")

ggsave(paste0(image_location, "/accuracy.png"))

d.utility %>% 
  filter(langUsed == "Lang") %>%
  ggplot(aes(x = repNum, y=prop_utility, color = as.factor(gameId))) + 
  geom_point(alpha = .4) + 
  facet_grid(cols = vars(blockNum), rows = vars(gameId)) + 
  #geom_smooth(method=glm, formula=y~poly(x,2), alpha=.3)+
  theme(legend.position = "none")+
  labs(title="Accuracy", y="Group utility/max utility", x="Round number", color="gameId") + ylim(0,1)

ggsave(paste0(image_location, "/accuracy.png"))
```

@@

```{r}
# ggplot(d.chat, aes(x=repNum, y=total_num_words, color=role))+
#   facet_wrap(~tangram, nrow=2)+
#   scale_color_brewer(palette="Dark2")+
#      stat_summary(fun.data = "mean_cl_boot")+
#   labs(title="Number of words", y="Number of words", x="Round number")+
#   theme(legend.position="bottom")
ggplot(d.chat, aes(x=repNum, y=total_num_words, color=as.factor(numPlayers)))+
  facet_wrap(~role, nrow=1)+
  scale_color_brewer(palette="Dark2")+
    geom_jitter(alpha=.05)+
    geom_smooth(method=glm, formula=y~poly(x,2), alpha=.3)+
  #geom_smooth(method = "glm", formula = y~x,method.args = list(family = gaussian(link = 'log')))+
     stat_summary(fun.data = "mean_cl_boot")+
    scale_y_continuous(limits = c(0,50))+
  labs(title="Number of words", y="Number of words", x="Round number", color="Player count")+
  theme(legend.position="bottom")
ggsave(here(image_location, 'words.pdf'), width=6, height=4)
```

```{r}
d.chat %>% filter(role=="speaker") %>% 
    mutate(groupxtangram=str_c(gameId,tangram)) %>% 
  group_by(repNum, numPlayers, gameId,tangram, groupxtangram) %>% 
  summarize(words=sum(total_num_words)) %>% 
ggplot(aes(x=repNum, y=words, color=as.factor(numPlayers)))+
  facet_wrap(~numPlayers, nrow=1)+
  scale_color_brewer(palette="Dark2")+
    geom_line(aes(group=groupxtangram), alpha=.1,method=glm, se=F)+
    geom_smooth(method = "glm", formula = y~x,method.args = list(family = gaussian(link = 'log')))+
    #geom_smooth(method=glm, formula=y~poly(x,2), alpha=.3)+
  labs(title="Words from speaker per tangram", y="Number of words", x="Round number", color="Player count")+
  theme(legend.position="null")
ggsave(here(image_location, 'words_lines.pdf'), width=6, height=4)
```

```{r}
d.chat %>% filter(role=="speaker") %>% 
ggplot(aes(x=repNum, y=total_num_words, color=as.factor(numPlayers)))+
  facet_wrap(~tangram)+
  scale_color_brewer(palette="Dark2")+
    #geom_smooth(method=glm, formula=y~poly(x,2), se=T, alpha=.1)+
      geom_smooth(method = "glm", formula = y~x,method.args = list(family = gaussian(link = 'log')))+
       stat_summary(fun.data = "mean_cl_boot", size=.2)+
  labs(title="Tangram variability", y="Number of words", x="Round number", color="Player count")+
  theme(legend.position="bottom")
ggsave(here(image_location, 'words_tangrams.pdf'), width=8, height=6)
```

>>>>

```{r set-up, include=F}
library(tidyverse)
library(jsonlite)
library(here)
source(here("code/preprocessing/00_preprocessing_functions.R"))
theme_set(theme_classic())

##Data import constants
date_start=lubridate::ymd('2021-07-19')
fig_path=here("figs")

@@

# Pre-process
Remove joined_data and uncomment the following block to rerun the preprocessing scripts
```{r process-data, message=FALSE, warning=FALSE}
data_list <- c("technical_pilots", "collabmulti_pilot0",
               "collabmulti_20", "compet_20")
process_all_data(data_list)
join_all_data()
```

```{r read-processed-date, message=FALSE}
d.players <- read_csv(here("data/processed_data/joined_data/players.csv"),
                      col_types = cols()) %>% distinct()
d.games <- read_csv(here("data/processed_data/joined_data/games.csv"),
                      col_types = cols()) %>% distinct()
d.rounds <- read_csv(here("data/processed_data/joined_data/rounds.csv"),
                      col_types = cols()) %>% distinct()
d.raw_chat <- read_csv(here("data/processed_data/joined_data/raw_chat.csv"),
                      col_types = cols()) %>% distinct()
d.contexts <- read_csv(here("data/processed_data/joined_data/contexts.csv"),
                      col_types = cols()) %>% distinct()
d.feedback <- read_csv(here("data/processed_data/joined_data/feedback.csv"),
                      col_types = cols()) %>% distinct()
d.demographics <- read_csv(here("data/processed_data/joined_data/demographics.csv"),
                      col_types = cols()) %>% distinct()
```

```{r}
#exclude BLOCKS with <12 completed (all 3 participants responded) rounds
#exclude trial runs

rounds_exclude <- d.rounds %>% group_by(gameId, blockNum) %>% tally() %>% filter(n!=36) %>% select(gameId,blockNum)

@@

```{r}
game_completion <- d.rounds %>% 
  group_by(gameId) %>% 
  summarize(num_rounds=max(trialNum+1)) %>% 
  left_join(d.games%>% ungroup() %>% select(gameId, condition, chat=chatEnabled, gameLength)) %>%
  mutate(gameComplete = ifelse(num_rounds == 48, TRUE, FALSE))
#knitr::kable(summary)
message("Full games")
game_completion %>% filter(num_rounds==48)
message("Partial games")
game_completion %>% filter(num_rounds!=48) 
```

Game counts
```{r}
#pull out pilots
d.games %>% group_by(condition, chatEnabled,pilot)%>% tally()
```

# Demographics
```{r demographics}
d.demographics
```

```{r feedback}
d.feedback
```

# Basic Analyses
## Simple Distributions

```{r}
#get the # of raw points, max adjusted points, game legnth, # of words exchanged
d.round_word_counts <- d.raw_chat.final %>% 
  filter(type == "message") %>%
  full_join(d.rounds.final, c("gameId", "trialNum", "repNum", 
                              "playerId", "numPlayers", "blockNum")) %>%
 # filter(!is.chitchat) %>% 
  mutate(text = gsub("\\n", '', fixed = T, text),
         text = gsub("[/?/.]", ' ', text),
         text = str_squish(text),
         utt_length_chars = str_length(text), 
         utt_length_words = str_count(text, "\\W+") + 1) %>% 
  group_by(gameId, blockNum, trialNum, repNum, playerId, numPlayers) %>%
  summarize(text = paste0(text, collapse = ', '),
            total_num_words = sum(utt_length_words),
            total_num_chars = sum(utt_length_chars))

d.by_game_metrics <- d.rounds.final%>% 
  left_join(d.games %>% select(-createdAt)) %>%  
  left_join(d.round_word_counts) %>%
  left_join(game_completion %>% select(gameId, num_rounds)) %>%
  mutate(languageCondition = ifelse(chatEnabled, "Lang", "Nonlang"),
         fullCondition = paste(condition, languageCondition, sep = "-")) %>% 
  #group by game
  group_by(gameId, name,condition, languageCondition, fullCondition, gameLength,num_rounds) %>%
  summarize(groupPoints = sum(playerUtility, na.rm = T),
            groupNumWords = sum(total_num_words, na.rm = T),
            groupNumChars = sum(total_num_chars, na.rm = T))%>%
  mutate(groupPoints = ifelse(condition=="coopCartel", 
                               groupPoints/3, groupPoints)) %>% 
  #adjust for max
  mutate(adjustedPoints = case_when(condition == "coopCartel" ~ groupPoints/ ((12*3)*48),
                                    condition == "coopMulti" ~ groupPoints/ ((12+11+10)*48),
                                    condition == "competCartel" ~ groupPoints/ ((12+11+10)*48)))
```

### Points

Unadjusted

```{r, fig.height=3, fig.width=5}
d.by_game_metrics%>% 
  ggplot(aes(x = languageCondition, y = groupPoints, color = condition, shape = languageCondition)) + 
  geom_jitter(width = .2, alpha = .5) +
  stat_summary(fun.data = "mean_cl_boot")+
  facet_grid(cols = vars(condition)) + labs(x = "Language Condition", y = "Points Earned by Group", title = "Points Earned by Group") + theme_classic() + theme(legend.position = "none")

ggsave(here(fig_path, "points_distirbution_raw.png"))
```

Max Adjusted

```{r, fig.height=3, fig.width=5}
d.by_game_metrics %>%
  ggplot(aes(x = languageCondition, y = adjustedPoints, color = condition, shape = languageCondition)) + 
  geom_jitter(width = .2, alpha = .5) +
  stat_summary(fun.data = "mean_cl_boot")+
  facet_grid(cols = vars(condition)) + labs(x = "Language Condition", y = "Points Earned by Group (Max Adjusted)", title = "Adjusted Points by Group") + theme_classic() + theme(legend.position = "none")

ggsave(here(fig_path, "points_distirbution_adjusted.png"))
```

### Time
```{r, fig.height=3, fig.width=5}
d.by_game_metrics %>%
  ggplot(aes(x = languageCondition, y = gameLength/60, color = condition, shape = languageCondition)) + 
  geom_jitter(width = .2, alpha = .5) +
  stat_summary(fun.data = "mean_cl_boot")+
  facet_grid(cols = vars(condition))+ labs(y = "Time (In Minutes)", title = "Game Length")+theme_classic() + theme(legend.position = "none")
```
```{r, fig.height=3, fig.width=5}
d.by_game_metrics %>%
  ggplot(aes(x = languageCondition, y = log(gameLength/60), color = condition, shape = languageCondition)) + 
  geom_jitter(width = .2, alpha = .5) +
  stat_summary(fun.data = "mean_cl_boot")+
  facet_grid(cols = vars(condition))+ labs(y = "Time (In Log Minutes)", title = "Game Length (Log Mins)")+theme_classic() + theme(legend.position = "none")
```

### Number of Words
```{r, fig.height=3, fig.width=5}
d.by_game_metrics %>%
  ggplot(aes(x = languageCondition, y = groupNumWords, color = condition, shape = languageCondition)) + 
  geom_jitter(width = .2, alpha = .5) +
  stat_summary(fun.data = "mean_cl_boot")+
  facet_grid(cols = vars(condition))+ labs(y = "N. Words", title = "Number of Words Exchanged")+theme_classic() + theme(legend.position = "none")
```
```{r, fig.height=3, fig.width=5}
d.by_game_metrics %>%
  ggplot(aes(x = languageCondition, y = log(groupNumWords), color = condition, shape = languageCondition)) + 
  geom_jitter(width = .2, alpha = .5) +
  stat_summary(fun.data = "mean_cl_boot")+
  facet_grid(cols = vars(condition))+ labs(y = "Log N. Words Exchanged")+theme_classic() + theme(legend.position = "none")
```

#### Condition Effects on Language Use
```{r}
d.round_word_counts %>%left_join(d.games %>% 
                                   select(gameId, condition,chatEnabled)) %>% 
  mutate(languageCondition = ifelse(chatEnabled, "Lang", "Nonlang"),
         fullCondition = paste(condition, languageCondition, sep = "-"),
         block_name = paste0("Block ", blockNum)) %>%
    filter(languageCondition == "Lang") %>%
  group_by(gameId, fullCondition, languageCondition, condition) %>% 
  summarize(groupNumWords = sum(total_num_words, na.rm = T)) %>% 
  ggplot() + geom_density(aes(x = groupNumWords, fill = condition), alpha = .5, adjust = .7)
```

## Scatters
### Time x Points
```{r, fig.height=3, fig.width=5}
d.by_game_metrics %>%
  ggplot(aes(x = gameLength/60, y = groupPoints, color = condition)) + 
  geom_point(alpha = .5) +
  geom_smooth(method=lm)+
  facet_grid(cols = vars(condition))+ labs(x = "Game length (in Minutes)", y = "Points Earned by Group")+theme_classic() + theme(legend.position = "none")
```

```{r, fig.height=3, fig.width=5}
d.by_game_metrics %>%
  ggplot(aes(x = gameLength/60, y = groupPoints, color = log(groupNumWords))) + 
  geom_point(alpha = .5) +
  geom_smooth(method=lm)+
  facet_grid(cols = vars(condition))+ labs(x = "Game length (in Minutes)", y = "Points Earned by Group")+theme_classic() + scale_color_steps()
```

```{r, fig.height=3, fig.width=5}
d.by_game_metrics %>%
  ggplot(aes(x = gameLength/60, y = groupPoints, color = condition)) + 
  geom_point(alpha = .5) +
  geom_smooth(method=lm)+
  labs(x = "Game length (in Minutes)", y = "Points Earned by Group")+theme_classic()
```

Log
```{r, fig.height=3, fig.width=5}
d.by_game_metrics %>% 
  ggplot(aes(x = log(gameLength/60), y = groupPoints, color = condition)) + 
  geom_point(alpha = .5) +
  geom_smooth(method=lm)+
  facet_grid(cols = vars(condition))+ labs(x = "Game length (in Log Minutes)",y = "Points Earned by Group")+theme_classic() + theme(legend.position = "none")
```
```{r, fig.height=3, fig.width=5}
d.by_game_metrics %>% 
  ggplot(aes(x = log(gameLength/60), y = groupPoints, color = condition)) + 
  geom_point(alpha = .5) +
  geom_smooth(method=lm)+
  labs(x = "Game length (in Log Minutes)",y = "Points Earned by Group")+theme_classic()
```
### Language x Points
#### Faceted
```{r, fig.height=3, fig.width=5}
d.by_game_metrics %>% filter(languageCondition == "Lang") %>%
  ggplot(aes(x = groupNumWords, y = groupPoints, color = condition)) + 
  geom_point(alpha = .5) +
  geom_smooth(method=lm)+
  facet_grid(cols = vars(condition))+ labs(x = "N. Words Exchanged", y = "Group Points (Raw)")+theme_classic() + theme(legend.position = "none")
```
```{r, fig.height=3, fig.width=5}
d.by_game_metrics %>% filter(languageCondition == "Lang") %>%
  ggplot(aes(x = groupNumWords, y = adjustedPoints, color = condition)) + 
  geom_point(alpha = .5) +
  geom_smooth(method=lm)+
  facet_grid(cols = vars(condition))+ labs(x = "N. Words Exchanged", y = "Group Points (Adjusted)")+theme_classic() + theme(legend.position = "none")
```
#### Non-Faceted
```{r, fig.height=3, fig.width=5}
d.by_game_metrics %>% filter(languageCondition == "Lang") %>%
  ggplot(aes(x = groupNumWords, y = groupPoints, color = condition)) + 
  geom_point(alpha = .5) +
  geom_smooth(method=lm)+
  labs(x = "N. Words Exchanged", y = "Group Points (Raw)")+theme_classic()
```
```{r, fig.height=3, fig.width=5}
d.by_game_metrics %>% filter(languageCondition == "Lang") %>%
  ggplot(aes(x = groupNumWords, y = adjustedPoints, color = condition)) + 
  geom_point(alpha = .5) +
  geom_smooth(method=lm)+
  labs(x = "N. Words Exchanged", y = "Group Points (Adjusted)")+theme_classic()
```

### Progress Over Time

Including language optional games where they decided not to speak

```{r, fig.height=3, fig.width=5}
d.round_word_counts %>%left_join(d.games %>% 
                                   select(gameId, condition,chatEnabled)) %>% 
  mutate(languageCondition = ifelse(chatEnabled, "Lang", "Nonlang"),
         fullCondition = paste(condition, languageCondition, sep = "-"),
         block_name = paste0("Block ", blockNum)) %>%
    filter(languageCondition == "Lang") %>%
  group_by(gameId, fullCondition,block_name, trialNum, repNum) %>% 
  summarize(groupNumWords = sum(total_num_words, na.rm = T)) %>%
  ggplot(aes(x = repNum, y = groupNumWords, color = fullCondition)) + 
  geom_point(alpha = .2) +
  geom_smooth(method=lm)+
  facet_grid(cols = vars(block_name)) + labs(x = "Trial Number", y = "N. Words")+ theme_classic()
```

log (n words+1)
```{r, fig.height=3, fig.width=5}
d.round_word_counts %>%left_join(d.games %>% 
                                   select(gameId, condition,chatEnabled)) %>% 
  mutate(languageCondition = ifelse(chatEnabled, "Lang", "Nonlang"),
         fullCondition = paste(condition, languageCondition, sep = "-"),
         block_name = paste0("Block ", blockNum)) %>%
    filter(languageCondition == "Lang") %>%
  group_by(gameId, fullCondition,block_name, trialNum, repNum) %>% 
  summarize(groupNumWords = sum(total_num_words, na.rm = T)+1) %>%
  ggplot(aes(x = repNum, y = log(groupNumWords), color = fullCondition)) + 
  geom_point(alpha = .2) +
  geom_smooth(method=lm)+
  facet_grid(cols = vars(block_name)) + labs(x = "Trial Number", y = "Log (N. Words + 1)")+ theme_classic()
```

Only games where language was used

```{r, fig.height=3, fig.width=5}
d.round_word_counts %>%left_join(d.games %>% 
                                   select(gameId, condition,chatEnabled)) %>% 
  mutate(languageCondition = ifelse(chatEnabled, "Lang", "Nonlang"),
         fullCondition = paste(condition, languageCondition, sep = "-"),
         block_name = paste0("Block ", blockNum)) %>%
    filter(languageCondition == "Lang") %>%
  group_by(gameId, fullCondition,block_name, trialNum, repNum) %>% 
  summarize(groupNumWords = sum(total_num_words, na.rm = T)) %>%
  filter(groupNumWords > 0) %>%
  ggplot(aes(x = repNum, y = groupNumWords, color = fullCondition)) + 
  geom_point(alpha = .2) +
  geom_smooth(method=lm)+
  facet_grid(cols = vars(block_name)) + labs(x = "Trial Number", y = "N. Words")+ theme_classic()
```

### Accuracy
#### N. Overlap

```{r}
# d.round_results.final %>% left_join(d.games %>% select(gameId, condition, chatEnabled, langUse, gameComplete)) %>%
#   mutate(chat = ifelse(chatEnabled, "lang", "nonlang"),
#          full_condition = paste0(condition, "-", chat)) %>%
#   ggplot(aes(x=time_sec, y = as.numeric(playerUtility), color = full_condition)) + 
#   facet_grid(rows = vars(condition), cols = vars(langUse)) +
#   geom_point(alpha = .25) + 
#   labs(x = "log time (in seconds)",
#        y = "individual utility",
#        title = "Response time in sec and utility", subtitle =  "each participant, each round")
# 
# d.round_results.final %>% left_join(d.games %>% select(gameId, condition, chatEnabled, langUse)) %>%
#   mutate(chat = ifelse(chatEnabled, "lang", "nonlang"),
#          full_condition = paste0(condition, "-", chat)) %>%
#   ggplot(aes(x=log(time_sec), y = as.numeric(playerUtility), color = full_condition)) + 
#   facet_grid(rows = vars(condition), cols = vars(langUse)) +
#   geom_point(alpha = .25) + 
#   labs(x = "log time (in seconds)",
#        y = "individual utility",
#        title = "Response time in sec (log) and utility", subtitle =  "each participant, each round")
```

@@

competcartel will have a max utility = sum(top_3_flowers)
```{r}
# d.max_utility <- d.contexts %>% 
#   left_join(d.games %>% select(gameId, condition)) %>%
#   mutate(utility= as.numeric(utility)) %>%
#   group_by(gameId, blockNum, repNum) %>% 
#   slice_max(order_by =utility,n = 3)%>%
#   summarize(competCartel = sum(utility),
#             coopMulti= sum(utility),
#             coopCartel = max(utility * 9)) %>% ungroup() %>%
#   pivot_longer(cols = c(competCartel, coopMulti, coopCartel), names_to = "condition", values_to = "maxUtility")
# 
# 
# d.utility <- d.round_results.final %>%
#          left_join(d.games %>% select(gameId, condition, chatEnabled, langUse)) %>% 
#   group_by(gameId, blockNum, repNum, trialNum,condition, langUse) %>% 
#   summarize(group_utility = sum(as.numeric(playerUtility)))%>% ungroup() %>%
#   left_join(d.max_utility) %>%
#   mutate(prop_utility = group_utility/maxUtility,
#          langUsed = if_else(langUse, "Lang", "Nonlang"))
# 
# d.utility %>% 
#   ggplot(aes(x = trialNum, y=prop_utility, color = as.factor(gameId))) + 
#   geom_point(alpha = .4) + 
#   facet_grid(cols = vars(condition), rows = vars(langUsed), scales = "free_y") + 
#   #geom_smooth(method=glm, formula=y~poly(x,2), alpha=.3)+
#   theme(legend.position = "none")+
#   labs(title="Accuracy", y="Group utility/max utility", x="Round number", color="gameId")
# 
# ggsave(paste0(image_location, "/accuracy.png"))
# 
# d.utility %>% 
#   ggplot(aes(x = trialNum, y=prop_utility, color = as.factor(gameId))) + 
#   geom_point(alpha = .4) + 
#   facet_grid(cols = vars(condition), rows = vars(langUsed), scales = "free_y") + 
#   #geom_smooth(method=glm, formula=y~poly(x,2), alpha=.3)+
#   theme(legend.position = "none")+
#   labs(title="Accuracy", y="Group utility/max utility", x="Round number", color="gameId")
# 
# ggsave(paste0(image_location, "/accuracy.png"))
# 
# d.utility %>% 
#   filter(langUsed == "Lang") %>%
#   ggplot(aes(x = repNum, y=prop_utility, color = as.factor(gameId))) + 
#   geom_point(alpha = .4) + 
#   facet_grid(cols = vars(blockNum), rows = vars(gameId)) + 
#   #geom_smooth(method=glm, formula=y~poly(x,2), alpha=.3)+
#   theme(legend.position = "none")+
#   labs(title="Accuracy", y="Group utility/max utility", x="Round number", color="gameId") + ylim(0,1)
# 
# ggsave(paste0(image_location, "/accuracy.png"))
```

@@

```{r}
# ggplot(d.chat, aes(x=repNum, y=total_num_words, color=role))+
#   facet_wrap(~tangram, nrow=2)+
#   scale_color_brewer(palette="Dark2")+
#      stat_summary(fun.data = "mean_cl_boot")+
#   labs(title="Number of words", y="Number of words", x="Round number")+
#   theme(legend.position="bottom")
# ggplot(d.chat, aes(x=repNum, y=total_num_words, color=as.factor(numPlayers)))+
#   facet_wrap(~role, nrow=1)+
#   scale_color_brewer(palette="Dark2")+
#     geom_jitter(alpha=.05)+
#     geom_smooth(method=glm, formula=y~poly(x,2), alpha=.3)+
#   #geom_smooth(method = "glm", formula = y~x,method.args = list(family = gaussian(link = 'log')))+
#      stat_summary(fun.data = "mean_cl_boot")+
#     scale_y_continuous(limits = c(0,50))+
#   labs(title="Number of words", y="Number of words", x="Round number", color="Player count")+
#   theme(legend.position="bottom")
# ggsave(here(image_location, 'words.pdf'), width=6, height=4)
```

```{r}
# d.chat %>% filter(role=="speaker") %>% 
#     mutate(groupxtangram=str_c(gameId,tangram)) %>% 
#   group_by(repNum, numPlayers, gameId,tangram, groupxtangram) %>% 
#   summarize(words=sum(total_num_words)) %>% 
# ggplot(aes(x=repNum, y=words, color=as.factor(numPlayers)))+
#   facet_wrap(~numPlayers, nrow=1)+
#   scale_color_brewer(palette="Dark2")+
#     geom_line(aes(group=groupxtangram), alpha=.1,method=glm, se=F)+
#     geom_smooth(method = "glm", formula = y~x,method.args = list(family = gaussian(link = 'log')))+
#     #geom_smooth(method=glm, formula=y~poly(x,2), alpha=.3)+
#   labs(title="Words from speaker per tangram", y="Number of words", x="Round number", color="Player count")+
#   theme(legend.position="null")
# ggsave(here(image_location, 'words_lines.pdf'), width=6, height=4)
```
